Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-21 paper.tex
Minor edits

Our evaluation (Sec.~\ref{sec:evaluation}) shows that this new implementation of forward reasoning in Aesop substantially outperforms the previous, naive implementation on synthetic benchmarks.
The implementation, benchmarks and evaluation data are available in a supplement to this paper~\cite{supplement} and the new implementation is already available for the newest version of Aesop.

@@

\para{Forward States.}
We associate with each goal in Aesop's search tree a forward state that reflects the goal's context.
Let $\States$ be the set of forward states, $\Hyps$ the set of hypotheses, $\Rules$ the set of rules, $\CMatches$ the set of complete matches and $\powerset(X)$ the powerset of $X$.
The forward state's interface then consists of two functions
\begin{equation*}
  \addHyp : \States → \Hyps → \States × \powerset(\Rules × \CMatches) \qquad \delHyp : \States → \Hyps → \States
\end{equation*}
The $\addHyp$ function adds a hypothesis to the forward state.
Hence, if $s$ is the forward state corresponding to context $Γ$ and $\addHyp(s,\, h : T) = (s', C)$, then $s'$ is the forward state corresponding to $Γ,\, h : T$.
Similarly, if $s$ is the forward state corresponding to $Γ, h : T$, then $\delHyp(s,\, h : T)$ is the forward state corresponding to $Γ$.
The second output of $\addHyp$, $C$, is a set of pairs $(r, m)$ where $r$ is a rule and $m$ is a complete match for $r$.
These are the matches that were completed by adding $h : T$.

>>>>

Our evaluation (Sec.~\ref{sec:evaluation}) shows that this new implementation of forward reasoning in Aesop substantially outperforms the previous, naive implementation on synthetic benchmarks.
The implementation, benchmarks and evaluation data are available in a supplement to this paper~\cite{supplement} and the new implementation is already available in the newest version of Aesop.

@@

\para{Forward States.}
We associate with each goal in Aesop's search tree a forward state that reflects the goal's context.
Let $\States$ be the set of forward states, $\Hyps$ the set of hypotheses, $\Rules$ the set of rules, $\CMatches$ the set of complete matches and $\powerset(X)$ the powerset of $X$.
The forward state's interface then consists of two functions
\begin{equation*}
  \addHyp : \States → \Hyps → \States × \powerset(\Rules × \CMatches) \qquad \delHyp : \States → \Hyps → \States
\end{equation*}
The $\addHyp$ function adds a hypothesis to the forward state.
Hence, if $s$ is the forward state corresponding to context $Γ$ and $\addHyp(s,\, h : T) = (s', C)$, then $s'$ is the forward state corresponding to $Γ,\, h : T$.
Similarly, if $s$ is the forward state corresponding to $Γ,\, h : T$, then $\delHyp(s,\, h : T)$ is the forward state corresponding to $Γ$.
The second output of $\addHyp$, $C$, is a set of pairs $(r, m)$ where $r$ is a rule and $m$ is a complete match for $r$.
These are the matches that were completed by adding $h : T$.
